Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-19 Documents/supplementary_text.tex
More hacking on supplement.

\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage{geometry}

@@

\usepackage[numbers, round, sort&compress]{natbib}
\renewcommand{\citenumfont}{\itshape}  % Citations get italics numbers
\makeatletter
\renewcommand\NAT@open{(\hspace*{-0.3ex}}   % Tweak spacing.
\renewcommand\@biblabel[1]{#1.}  % Reference list doesn't use square brackets.
\makeatother

@@

% Load hyperref after the other stuff above.
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{hypernat}

@@

We developed a continuous-time, compartmental model that divides
people aged 15 years and older into 8 health states
(\autoref{model_diag}): susceptible to HIV infection ($S$), vaccinated
against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
infection ($U$), diagnosed but untreated HIV infection ($D$), treated
without viral suppression ($T$), viral suppression ($V$), and having
AIDS ($W$).  We chose to consider only people aged 15 years and older
because they are the vast majority of PLHIV (93\% in 2014
\cite{UNICEF}).  Transitions between states are governed by a series
of differential equations parametrized using rates estimated from
other studies and from incidence and prevalence data (Table
\ref{model_param}).  The model is deterministic, but uncertainty in
the parameters is treated by running the model with many different
samples from the parameter distributions and summarizing the model
outcomes using the median, 1st and 3rd quartiles (i.e., 25th and 75th
percentiles), and 5th and 95th percentiles.

@@

The background mortality rate ($\mu$) in each of the 127 countries was
collected from published estimates
\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
the 15 age group was 
including population
growth rate \cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd}

@@

@@

\clearpage
\bibliographystyle{science_nat}
\bibliography{supplementary_text}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{geometry}

@@

@@

\usepackage[pdfborder={0 0 0}]{hyperref}

\usepackage[style = science, article-title = true, maxnames = 100]{biblatex}
\addbibresource{supplementary_text.bib}
\newcommand{\labeltitlepunc}{}
\DeclareBibliographyDriver{incollection}{%
  \usebibmacro{bibindex}%
  \usebibmacro{begentry}%
  \usebibmacro{author/translator+others}%
  \setunit{\labelnamepunct}\newblock
  \printlist{language}%
  \newunit\newblock
  \usebibmacro{byauthor}%
  \newunit\newblock
  \usebibmacro{title}%
  \usebibmacro{in:}%
  \usebibmacro{maintitle+booktitle}%
  \newunit\newblock
  \usebibmacro{byeditor+others}%
  \newunit\newblock
  \printfield{volumes}%
  \newunit\newblock
  \printfield{note}%
  \newunit\newblock
  \usebibmacro{publisher+location+date}%
  \newunit\newblock
  \printfield{volume}
  \newunit
  \usebibmacro{chapter+pages}%
  \newunit\newblock
  \iftoggle{bbx:isbn}
    {\printfield{isbn}}
    {}%
  \newunit\newblock
  \usebibmacro{doi+eprint+url}%
  \newunit\newblock
  \usebibmacro{addendum+pubstate}%
  \setunit{\bibpagerefpunct}\newblock
  \usebibmacro{pageref}%
  \newunit\newblock
  \usebibmacro{related}%
  \usebibmacro{finentry}%
}

@@

We developed a continuous-time, compartmental model that divides
people aged $15\;\text{y}$ and older into 8 health states
(\autoref{model_diag}): susceptible to HIV infection ($S$), vaccinated
against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
infection ($U$), diagnosed but untreated HIV infection ($D$), treated
without viral suppression ($T$), viral suppression ($V$), and having
AIDS ($W$).  We chose to consider only people aged $15\;\text{y}$ and
older because they are the vast majority of PLHIV, 93\% in 2014
\cite{UNICEF}, and because HIV and demographic data are often
stratified into these ages \cite[e.g.,][]{Unaids2016-an}.  Transitions
between model states are governed by a series of differential
equations parametrized using rates estimated from other studies and
from incidence and prevalence data (Table \ref{model_param}).  The
model is deterministic, but uncertainty in the parameters is treated
by running the model with many different samples from the parameter
distributions and summarizing the model outcomes using the median, 1st
and 3rd quartiles (i.e., 25th and 75th percentiles), and 5th and 95th
percentiles.

@@

@@

The background mortality rate ($\mu$) in each of the 127 countries was
collected from published estimates
\cite{World_Development_Indicators2013-ee}.  The recruitment rate into
ages $15\;\text{y}$ and older group ($B$) was set by the difference
between the population growth rate \cite{WorldBankpg} and the
background mortality rate \cite{World_Development_Indicators2013-ee}.
\comment{Add mortality and population growth to data sources.}

The number of people aged 15--49 years \cite{The_World_Bank2016-fd}

@@

\clearpage
\printbibliography
